Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-04-08 WSSSPE1_report/WSSSPE1_summary_report.tex
Changes to mainly first page. Minor changes to section titles.

\usepackage{color}
\usepackage{dcolumn}
\usepackage{float}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{rotating}
\usepackage{subfigure}
\usepackage{psfrag}
\usepackage{tabularx}
\usepackage[hyphens]{url}
\usepackage{wrapfig}
\usepackage{enumitem}
\usepackage{multicol}

@@

\author{Authors TBD}

%\author{Daniel S. Katz$^{(1)}$, Gabrielle Allen$^{(2)}$, Neil Chue Hong$^{(3)}$, \\
%Manish Parashar$^{(4)}$, and David Proctor$^{(1)}$ }
%
%
%\thanks{{}$^{(1)}$ National Science Foundation, Arlington, VA, USA}
%
%\thanks{{}$^{(2)}$ Skolkovo Institute of Science and Technology, Moscow, Russian Federation}
%
%\thanks{{}$^{(3)}$ Software Sustainability Institute, University of Edinburgh, Edinburgh, UK}
%
%\thanks{{}$^{(4)}$ Rutgers Discovery Informatics Institute, Rutgers University, New Brunswick, NJ, USA}

\begin{abstract}
This document discusses the First Workshop on Sustainable
Software for Science: Practice and Experiences (WSSSPE1).  The content
is based on the workshop itself, as recorded in a set of
collaborative notes taken during the workshop, including discussion
about the keynote presentations, three themed panels that focus on
papers accepted by the workshop, other discussion, cross-cutting
issues, use cases, and conclusions.  It joins a nascent literature
seeking to understand what drives software work in science and how the
reward systems of science thereby shapes the type of software work
undertaken, including the extent to which developers are motivated to
build software for the long-term, for the use of others, and whether
to work collaboratively or separately. Unique perspectives were
captured about issues such as documentation of APIs, software
deployment, and development practices; software licenses; career
paths for scientific software developers; identifiers for software
through a mechanism such as a Digital Object Identifier or
publication of a ``software paper''; and evidence of software
contribution and impact, recorded in online systems such as source
code repositories like GitHub. For truly sustainable software there
should be no endpoint, as the software products continue to be used
and useful beyond the single institution, grant, and developer or
development team.

@@

People who have volunteered to work on this report: (with * for actual
contributors - \note{if you contribute, add a * by your name})

@@

Additional volunteers:
\begin{itemize}
% \item Chris Mattmann $\langle$\url{chris.a.mattmann@jpl.nasa.gov}$\rangle$
\item * Ketan Maheshwari $\langle$\url{ketancmaheshwari@gmail.com}$\rangle$
\item Marlon Pierce $\langle$\url{marpierc@iu.edu}$\rangle$
\item * Colin Venters $\langle$\url{C.Venters@hud.ac.uk}$\rangle$
\item Suresh Marru $\langle$\url{smarru@iu.edu}$\rangle$
% \item Lynn Zentner $\langle$\url{lzentner@purdue.edu}$\rangle$
\item Anne Elster $\langle$\url{anne.elster@gmail.com}$\rangle$
\item * Shel Swenson $\langle$\url{mdswenso@usc.edu}$\rangle$
\item * Andy Ray Terrel $\langle$\url{andy.terrel@gmail.com}$\rangle$
% \item Abani Patra $\langle$\url{abani.patra@gmail.com}$\rangle$
\item * Nancy Wilkins-Diehr $\langle$\url{wilkinsn@sdsc.edu}$\rangle$
% \item James Spencer $\langle$\url{j.spencer@imperial.ac.uk}$\rangle$
\item * Frank L\"{o}ffler $\langle$\url{knarf@cct.lsu.edu}$\rangle$
\item * James Hetherington $\langle$\url{j.hetherington@ucl.ac.uk}$\rangle$
\item * Sou-Cheng (Terrya) Choi $\langle$\url{sou.cheng.terrya.choi@gmail.com}$\rangle$
\item * James Howison $\langle$\url{james@howison.name}$\rangle$
\item * Bruce Berriman $\langle$\url{gbb@ipac.caltech.edu}$\rangle$
\item * Hilmar Lapp $\langle$\url{hlapp@nescent.org}$\rangle$
\item * Marcus D. Hanwell $\langle$\url{marcus.hanwell@kitware.com}$\rangle$
\item Lucas Nussbaum $\langle$\url{lucas.nussbaum@loria.fr}$\rangle$
\item * Matthew Turk $\langle$\url{matthewturk@gmail.com}$\rangle$
\end{itemize}

The original document is
\url{https://docs.google.com/document/d/1eVfioGNlihXG_1Y8BgdCI6tXZKrybZgz5XuQHjT1oKU/edit?pli=1#}
(but can no longer be edited).  Note that the original document has
comments in addition to text.

@@

\section{Keynotes \note{lead: Sou-Cheng (Terrya) Choi} } \label{sec:keynotes}

@@

\section{Developing and Supporting Software \note{lead: Marcus Hanwell, contributors: Suresh Marru}} \label{sec:devel}

@@

\section{Communities \note{lead: Matthew Turk, contributors: Nancy Wilkins-Diehr, Chris Mattmann, Suresh Marru, Frank L\"{o}ffler, Andy Terrel}} \label{sec:community}

@@

The literature below, suggested by attendees, addresses both non-scientific
software projects, as well as scientific projects.  The selections address both
descriptive and prescriptive approaches to communities.

>>>>

\usepackage{color}
\usepackage{dcolumn}
\usepackage{float}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{rotating}
\usepackage{subfigure}
\usepackage{psfrag}
\usepackage{tabularx}
\usepackage[hyphens]{url}
\usepackage{wrapfig}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{verbatim}

@@

\author{Bruce Berriman$^{(1)}$, Sou-Cheng T. Choi$^{(2)}$, Marcus D. Hanwell$^{(3)}$, James Hetherington$^{(4)}$, James Howison$^{(5)}$, Daniel S. Katz$^{(6)}$, Hilmar Lapp$^{(7)}$, Frank L\"{o}ffler$^{(8)}$, Ketan Maheshwari$^{(9)}$, Shel Swenson$^{(10)}$,  Andy R. Terrel$^{(11)}$, Matthew Turk$^{(12)}$,  Colin Venters$^{(13)}$, Nancy Wilkins-Diehr$^{(14)}$}
\note{Authors, please add/check middle initials and affliations.  For now, the order is alphabetical for now  because Choi does not know how to count...}

\thanks{{}$^{(1)}$ xxx}
%
\thanks{{}$^{(2)}$ NORC at the University of Chicago and the Illinois Institute of Technology, Chicago, IL, USA (\url{sctchoi@uchicago.edu}}
% 
\thanks{{}$^{(3)}$ xxx}
%
\thanks{{}$^{(4)}$ xxx}
%
\thanks{{}$^{(5)}$ xxx}
%
\thanks{{}$^{(6)}$ National Science Foundation, Arlington, VA, USA}
%
\thanks{{}$^{(7)}$ xxx}
%
\thanks{{}$^{(8)}$ xxx}
%
\thanks{{}$^{(9)}$ xxx}
%
\thanks{{}$^{(10)}$ xxx}
%
\thanks{{}$^{(11)}$ xxx}
%
\thanks{{}$^{(12)}$ xxx}
%
\thanks{{}$^{(13)}$ xxx}
%
\thanks{{}$^{(14)}$ xxx}

\begin{abstract} \note{Lead: Sou-Cheng T. Choi}
This document discusses the First Workshop on Sustainable
Software for Science: Practice and Experiences (WSSSPE1).  The content
is based on the workshop itself, as recorded in a set of
collaborative notes taken during the workshop, including discussion
about the keynote presentations, three themed panels that focus on
papers accepted by the workshop, other discussion, cross-cutting
issues, use cases, and conclusions.  It joins a nascent literature
seeking to understand what drives software work in science and how the
reward systems of science thereby shapes the type of software work
undertaken, including the extent to which developers are motivated to
build software for the long-term, for the use of others, and whether
to work collaboratively or separately. Unique perspectives were
captured about issues such as documentation of APIs, software
deployment, and development practices; software licenses; career
paths for scientific software developers; identifiers for software
through a mechanism such as a Digital Object Identifier or
publication of a ``software paper''; and evidence of software
contribution and impact, recorded in online systems such as source
code repositories like GitHub. For truly sustainable software there
should be no endpoint, as the software products continue to be used
and useful beyond the single institution, grant, and developer or
development team.

@@

\begin{comment}
People who have volunteered to work on this report: (with * for actual
contributors - \note{if you contribute, add a * by your name})

@@

Additional volunteers:
\begin{itemize}
% \item Chris Mattmann $\langle$\url{chris.a.mattmann@jpl.nasa.gov}$\rangle$
\item * Ketan Maheshwari $\langle$\url{ketancmaheshwari@gmail.com}$\rangle$
\item Marlon Pierce $\langle$\url{marpierc@iu.edu}$\rangle$
\item * Colin Venters $\langle$\url{C.Venters@hud.ac.uk}$\rangle$
\item Suresh Marru $\langle$\url{smarru@iu.edu}$\rangle$
% \item Lynn Zentner $\langle$\url{lzentner@purdue.edu}$\rangle$
\item Anne Elster $\langle$\url{anne.elster@gmail.com}$\rangle$
\item * Shel Swenson $\langle$\url{mdswenso@usc.edu}$\rangle$
\item * Andy Ray Terrel $\langle$\url{andy.terrel@gmail.com}$\rangle$
% \item Abani Patra $\langle$\url{abani.patra@gmail.com}$\rangle$
\item * Nancy Wilkins-Diehr $\langle$\url{wilkinsn@sdsc.edu}$\rangle$
% \item James Spencer $\langle$\url{j.spencer@imperial.ac.uk}$\rangle$
\item * Frank L\"{o}ffler $\langle$\url{knarf@cct.lsu.edu}$\rangle$
\item * James Hetherington $\langle$\url{j.hetherington@ucl.ac.uk}$\rangle$
\item * Sou-Cheng (Terrya) Choi $\langle$\url{sctchoi@uchicago.edu}$\rangle$
\item * James Howison $\langle$\url{james@howison.name}$\rangle$
\item * Bruce Berriman $\langle$\url{gbb@ipac.caltech.edu}$\rangle$
\item * Hilmar Lapp $\langle$\url{hlapp@nescent.org}$\rangle$
\item * Marcus D. Hanwell $\langle$\url{marcus.hanwell@kitware.com}$\rangle$
\item Lucas Nussbaum $\langle$\url{lucas.nussbaum@loria.fr}$\rangle$
\item * Matthew Turk $\langle$\url{matthewturk@gmail.com}$\rangle$
\end{itemize}

The original document is
\url{https://docs.google.com/document/d/1eVfioGNlihXG_1Y8BgdCI6tXZKrybZgz5XuQHjT1oKU/edit?pli=1#}
(but can no longer be edited).  Note that the original document has
comments in addition to text.
\end{comment}

@@

\section{Keynotes \note{lead: Sou-Cheng (Terrya) Choi}} \label{sec:keynotes}

@@

\section{Developing and Supporting Software \note{\scriptsize lead: Marcus Hanwell, contributor: Suresh Marru}} \label{sec:devel}

@@

\section{Communities \note{\vspace{-1ex}\tiny lead: Matthew Turk, contributors: Nancy Wilkins-Diehr, Chris Mattmann, Suresh Marru, Frank L\"{o}ffler, Andy Terrel}} \label{sec:community}

@@

The literature below, suggested by attendees, addresses both non-scientific
software projects, as well as scientific projects.  The selections address both
descriptive and prescriptive approaches to communities. \note{Choi: Do we need to itemize the reference numbers below? Please collapse them into a comma seperated list with a short description for all or each of the papers.
}
